\section{Intrinsic challenges of Grid Computing}
While designing a Grid system, intrinsic challenges have to be taken in consideration; that means that these challenges exist in Grid Computing independently of the inclusion of mobile devices or operating with just desktop computers. This section presents a list of the main challenges that a Grid system must face.
\vspace{20mm}

\subsection{Interoperability}
As mentioned in \textit{section \ref{layered_grid_architecture}}, interoperability among any potential participant is the central issue when designing a Grid Architecture, requiring a meticulous focus on designing reliable and versatile protocols for interaction.

Unless the system is designed with the limitation of utilizing a set of identical machines, which is not desirable, machines connected to a Grid operate with \textbf{different hardware}; this differentiation requires a layer of abstraction that separates the functioning of the Grid from the interaction with a single physical node that will use a specific implementation of the standardized Fabric layer.

But machines not only offer different hardware, they differentiate each other in general by the resource they offer. In the context of distributed execution of computational tasks, for example, nodes offer \textbf{different programming languages} that they are capable of executing. This becomes a problem for interoperability since a requestor might want to execute some task with an implementation in some specific programming language to respect a performance requirement or just because that language offers useful libraries for that particular task. While an implementation of a Fabric layer using a language that is capable of running on almost any device (such as JavaScript) is certainly possible, this creates a great limitation in the Grid's use cases related to distributed computing while at the same time constraining the architecture to a specific technology, which is bad while designing any software.

Obviously, an important interoperability issue comes from the fact that \textbf{nodes can utilize any operating system}, implying different ways of installing the software necessary to run the node's tasks and, most importantly, a differentiation with the interaction with the file system and the security mechanisms specific for that particular OS.

Another resource where nodes differ is the network capabilities that they can offer. Even though this is not a differentiation, in a narrow sense, that comes from the machine in itself but from the environment where it operates, this still becomes an interoperability problem inside a Grid system; for this reason the architecture has to be designed taking in consideration that different nodes will offer \textbf{different levels of reliability and speed for their network connection}, requiring mechanisms for handling errors, disconnections and distributing work accordingly to the network's speed of the node. 

\subsection{Security}
Security is an essential prerequisite in every system and the Grid makes no exception. First of, in order to access to the Grid it is necessary to have an authentication mechanism (as discussed in section \textit{\ref{connectivity_layer}}); said mechanism must \textbf{uniquely identify every user/entity alongside their unique machines inside the Grid}. While being fundamental in order to grant security, this mechanism is also required by the resources discovery and selection problem (\textit{section \ref{resources_discovery_and_selection}}).

Having a unique identity given by the authentication is also required for another important security problem: respecting resources \textbf{access policies} defined by the nodes providers. Said policies define what resources are offered by a machine, as well as who is authorized to use them. 

Unique identification becomes even more important when it is applied to requestors of the services of the Grid. In order to grant the security of volunteers that offer their machines, \textbf{when a user or an entity request a service, it must be trustable (verified) and accountable}; While it is important that also contributors are verified and accountable, this is a lesser concern considering that they can only act as passive entities.

Regarding \textbf{privacy} once authentication is granted it is also important that communications between entities inside the Grid are encrypted in order to avoid attacks from malicious entities that could intercept packets.

Finally, countermeasures has to be taken in order to \textbf{avoid the execution of malicious code}; despite the accountability of uniquely identified users helps to reduce this possibility, in is fundamental implementing security measures for avoiding the access to everything that is outside the defined access policies.

\subsection{Geographical distribution}
TODO

\subsection{Scalability and load balancing}
TODO

\subsection{Fault tolerance and Quality of Service (QoS)}
TODO

\subsection{Dynamic sharing relationships}
TODO

\subsection{Resources discovery and selection}\label{resources_discovery_and_selection}
TODO

\subsection{Job scheduling, replication, migration and monitoring}
TODO
